### 2024-03-26 appendix_exp1.Rmd
major changes before adding analytical part

@@

Figure \@ref(fig:exp1-plot) visualizes the results and table \@ref(tab:exp1-table) contains descriptive results.

@@

>>>>

```{r simuli, include=FALSE, out.width= "40%", fig.align="center", fig.show="hold"}
# knitr::include_graphics("figures/example_stimulus_exp1_convergent.png")
# knitr::include_graphics("figures/example_stimulus_exp1_divergent.png")
```

@@

Figure \@ref(fig:exp1-plot) visualizes the results and table \@ref(tab:exp1-table) contains descriptive results. Figure \@ref(fig:exp1-outcomes) visualizes score differences between the two outcomes, accuracy and competence.

@@

## Research questions

We had three additional research questions regarding the number of informants:

***RQ1: Do H1 and H2 hold for both a small [3] and a large [10] number of estimates?***

***RQ2: When making a guess based on the opinions of (independent) informants, will participants be more confident about their guess when there is a larger number of estimates compared to when this number is smaller?***

***RQ3: Is there an interaction effect between the number of estimates and convergence on perceived competence of informants?***

Regarding RQ1, we ran the same mixed models as for the two hypotheses, but without number as a covariate. Instead, we ran separate models for the three and the ten informants conditions. We find that for both sub-samples, there is a positive effect of convergence on both accuracy ($\hat{b}_{\text{three informants}}$ = `r exp1_research_questions$model_small_accuracy$convergenceconvergent$estimate` `r exp1_research_questions$model_small_accuracy$convergenceconvergent$ci`, p = `r exp1_research_questions$model_small_accuracy$convergenceconvergent$p.value`; $\hat{b}_{\text{ten informants}}$ = `r exp1_research_questions$model_large_accuracy$convergenceconvergent$estimate` `r exp1_research_questions$model_large_accuracy$convergenceconvergent$ci`, p = `r exp1_research_questions$model_large_accuracy$convergenceconvergent$p.value`) and competence ($\hat{b}_{\text{three informants}}$ = `r exp1_research_questions$model_small_competence$convergenceconvergent$estimate` `r exp1_research_questions$model_small_competence$convergenceconvergent$ci`, p = `r exp1_research_questions$model_small_competence$convergenceconvergent$p.value`; $\hat{b}_{\text{ten informants}}$ = `r exp1_research_questions$model_large_competence$convergenceconvergent$estimate` `r exp1_research_questions$model_large_competence$convergenceconvergent$ci`, p = `r exp1_research_questions$model_large_competence$convergenceconvergent$p.value`).

To test the other two research questions, we ran the same mixed-models as for the hypotheses, but this time including an interaction between number of informants and convergence. We use deviation-coded versions of our convergent variable (divergent = -0.5, convergent = 0.5), allowing us to have a coefficient measuring the main effect of the number of informants in our model. Regarding RQ2, pooling across convergent and divergent conditions, we find a main effect of number, such that participants had more confidence in their estimate when they relied on ten informants compared to three informants ($\hat{b}_{\text{Accuracy}}$ = `r exp1_research_questions$model_interaction_accuracy$number_effect_code$estimate` `r exp1_research_questions$model_interaction_accuracy$number_effect_code$ci`, p = `r exp1_research_questions$model_interaction_accuracy$number_effect_code$p.value`). Regarding RQ3, we find an interaction between number of informants and convergence on competence: the positive effect of convergence was stronger in scenarios involving ten informants compared to three informants ($\hat{b}_{\text{Competence}}$ = `r exp1_research_questions$model_interaction_competence$interaction$estimate` `r exp1_research_questions$model_interaction_competence$interaction$ci`, p = `r exp1_research_questions$model_interaction_competence$interaction$p.value`). We do not find a statistically significant interaction on accuracy ($\hat{b}_{\text{Accuracy}}$ = `r exp1_research_questions$model_interaction_accuracy$interaction$estimate` `r exp1_research_questions$model_interaction_accuracy$interaction$ci`, p = `r exp1_research_questions$model_interaction_accuracy$interaction$p.value`).

(ref:exp1-outcomes) Differences between accuracy and competence ratings, by level of convergence.

```{r exp1-outcomes, fig.cap="(ref:exp1-outcomes)"}
# Differences in outcome between accuracy and competence
exp1_long <- exp1 %>%
  pivot_longer(cols = c(confidence, competence), 
               names_to = "outcome", 
               values_to = "score")

interaction_plot <- ggplot(exp1_long, aes(x = outcome, y = score, 
                                         fill = convergence, 
                                         shape = convergence, 
                                         group = convergence, 
                                         color = convergence)) +
  scale_x_discrete(limits = c("confidence", "competence"), 
                   labels = c("Accuracy", "Competence")) +
  geom_half_violin(data = exp1_long %>% filter(outcome == "confidence"), 
                   position = position_nudge(x = -.2), adjust = 2, alpha = .4,
                   side = "l") +
  geom_half_violin(data = exp1_long %>% filter(outcome == "competence"),
                   position = position_nudge(x = .2), adjust = 2, alpha = .4,
                   side = "r") +
  xlab("Outcome") +
  ylab("Score") +
  scale_y_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7)) +
  stat_summary(fun = "mean", geom = "point", size = 3) +
  stat_summary(fun = "mean", geom = "line") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
  scale_fill_manual(name = NULL,
                    labels = c("divergent", "convergent"),
                    values = c("#E69F00", "#56B4E9")) +
  scale_color_manual(name = NULL,
                     labels = c("divergent", "convergent"),
                     values = c("#E69F00", "#56B4E9")) +
  guides(shape = "none",
         fill = guide_legend(title = NULL)) +
  plot_theme +
  # change font sizes
  theme(axis.text = element_text(size = 10)) +
  theme(axis.title = element_text(size = 15)) +
  theme(legend.text = element_text(size = 10))

print(interaction_plot)
```

```{r, include = FALSE}
# manual version for points / confidence intervals for the above plot

# exp1_long <- exp1 %>%
#   pivot_longer(cols = c(confidence, competence), 
#                names_to = "outcome", 
#                values_to = "score")
# 
# # Calculate mean and standard error
# mean_se <- exp1_long %>%
#   group_by(outcome, convergence) %>%
#   summarize(mean_score = mean(score), 
#             se_score = sd(score) / sqrt(n())) %>% 
#   mutate(ci_low = mean_score - se_score, 
#          ci_high = mean_score + se_score)
# 
# interaction_plot <- ggplot(exp1_long, aes(x = outcome, y = score, 
#                                          fill = convergence, 
#                                          shape = convergence, 
#                                          group = convergence, 
#                                          color = convergence)) +
#   scale_x_discrete(limits = c("confidence", "competence"), 
#                    labels = c("Accuracy", "Competence")) +
#   geom_half_violin(data = exp1_long %>% filter(outcome == "confidence"), 
#                    position = position_nudge(x = -.2), adjust = 2, alpha = .4,
#                    side = "l") +
#   geom_half_violin(data = exp1_long %>% filter(outcome == "competence"),
#                    position = position_nudge(x = .2), adjust = 2, alpha = .4,
#                    side = "r") +
#   xlab("Outcome") +
#   ylab("Score") +
#   scale_y_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7)) +
#   geom_point(data = mean_se, aes(x = outcome, y = mean_score), size = 3) +
#   geom_line(data = mean_se, aes(x = outcome, y = mean_score)) +
#   geom_errorbar(data = mean_se,
#                 aes(x = outcome,
#                     y = mean_score,
#                     ymin = mean_score - se_score,
#                     ymax = mean_score + se_score),
#                 width = 0.2) +
#   scale_fill_manual(name = NULL,
#                     labels = c("divergent", "convergent"),
#                     values = c("#E69F00", "#56B4E9")) +
#   scale_color_manual(name = NULL,
#                      labels = c("divergent", "convergent"),
#                      values = c("#E69F00", "#56B4E9")) +
#   guides(shape = "none",
#          fill = guide_legend(title = NULL)) +
#   plot_theme +
#   # change font sizes
#   theme(axis.text = element_text(size = 10)) +
#   theme(axis.title = element_text(size = 15)) +
#   theme(legend.text = element_text(size = 10))
# 
# print(interaction_plot)
```

### 2024-03-26 appendix_exp2.Rmd
major changes before adding analytical part

```{r exp2-conditions}
# The different introductions that participants read before seeing the sets of estimates, according to the conditions 
data.frame(
  Condition = c("Independence", "Discussion"),
  Description = c(
    "Players are asked to make completely independent decisions – they cannot see each other’s estimates, or talk with each other before giving their estimates.",
    "Players are asked to talk with each other about the game at length before giving their estimates."
  )
) #%>% 
  # apa_table(align = c("m{3cm}", "m{12cm}")) 
```

>>>>

```{r exp2-conditions}
# The different introductions that participants read before seeing the sets of estimates, according to the conditions 
data.frame(
  Condition = c("Independence", "Discussion"),
  Description = c(
    "Players are asked to make completely independent decisions – they cannot see each other’s estimates, or talk with each other before giving their estimates.",
    "Players are asked to talk with each other about the game at length before giving their estimates."
  )
) %>% 
  apa_table(align = c("m{3cm}", "m{12cm}")) 
```

### 2024-03-26 appendix_exp3.Rmd
major changes before adding analytical part

```{r conditions-exp3}
# The different introductions that participants read before seeing the sets of estimates, according to the conditions 
data.frame(
  Condition = c("Independence", "Conflict of interest"),
  Description = c(
    "Experts are independent of each other, and have no conflict of interest in predicting the stock value - they do not personally profit in any way from any future valuation of the stock.",
    "All three experts have invested in the specific stock whose value they are predicting, and they benefit if other people believe that the stock will be valued at [mean of respective distribution] in the future."
  )
) #%>% 
  # apa_table(align = c("m{3cm}", "m{12cm}"))  
```

@@

To minimize confounding of convergence with a certain placement of the center value, we paired center values with conditions such that each condition appears once in each half of the scale and each condition gets one of the extreme values. For example, in one set the convergence condition would get assigned center values of 1300 and 1570, the divergent condition center values of 1430 and 1700). We generated four such series (all possible combinations) and randomly assigned participants to one of them. Additionally, for each participant, we randomize the order of appearance of the sets of predictions within the respective series.

>>>>

```{r conditions-exp3}
# The different introductions that participants read before seeing the sets of estimates, according to the conditions 
data.frame(
  Condition = c("Independence", "Conflict of interest"),
  Description = c(
    "Experts are independent of each other, and have no conflict of interest in predicting the stock value - they do not personally profit in any way from any future valuation of the stock.",
    "All three experts have invested in the specific stock whose value they are predicting, and they benefit if other people believe that the stock will be valued at [mean of respective distribution] in the future."
  )
) %>% 
  apa_table(align = c("m{3cm}", "m{12cm}")) 
```

@@

To minimize confounding of convergence with a certain placement of the center value, we paired center values with conditions such that each condition appears once in each half of the scale and each condition gets one of the extreme values. For example, in one set the convergence condition would get assigned center values of 1300 and 1570, the divergent condition center values of 1430 and 1700). We generated four such series (all possible combinations) and randomly assigned participants to one of them. Additionally, for each participant, we randomized the order of appearance of the sets of predictions within the respective series.

### 2024-03-26 appendix_exp4.Rmd
major changes before adding analytical part

```{r exp4-stimuli, echo=FALSE}
# Create a matrix of image file paths as Markdown-formatted strings
image_paths <- data.frame(condition = c("opposing majority (0)", 
                                        "dissensus (1)", "majority (2)", 
                                        "consensus (3)"),
                          imgage_a = c("![](Experiment_4/figures/stimuli/opp_majority_a.png){ width=60% }", 
                        "![](Experiment_4/figures/stimuli/divergence_a.png){ width=60% }",
                        "![](Experiment_4/figures/stimuli/majority_a.png){ width=60% }", 
                        "![](Experiment_4/figures/stimuli/consensus_a.png){ width=60% }"),
                        imgage_b = c("![](Experiment_4/figures/stimuli/opp_majority_b.png){ width=60% }", 
                        "![](Experiment_4/figures/stimuli/divergence_b.png){ width=60% }",
                        "![](Experiment_4/figures/stimuli/majority_b.png){ width=60% }", 
                        "![](Experiment_4/figures/stimuli/consensus_b.png){ width=60% }"))

# Use kable() to create the table and print it as Markdown
kableExtra::kable(image_paths, format = "markdown",
                  col.names = c("Level", "Version a)", "Version b)"), 
                  align = "c",
                  caption = "All stimuli by levels of convergence")

@@

Table \@ref(tab:exp4-table) contains descriptive results.

@@

>>>>

```{r exp4-stimuli, echo=FALSE}
# Create a matrix of image file paths as Markdown-formatted strings
image_paths <- data.frame(condition = c("minority (0)", 
                                        "dissensus (1)", "majority (2)", 
                                        "consensus (3)"),
                          imgage_a = c("![](Experiment_4/figures/stimuli/opp_majority_a.png){ width=60% }", 
                        "![](Experiment_4/figures/stimuli/divergence_a.png){ width=60% }",
                        "![](Experiment_4/figures/stimuli/majority_a.png){ width=60% }", 
                        "![](Experiment_4/figures/stimuli/consensus_a.png){ width=60% }"),
                        imgage_b = c("![](Experiment_4/figures/stimuli/opp_majority_b.png){ width=60% }", 
                        "![](Experiment_4/figures/stimuli/divergence_b.png){ width=60% }",
                        "![](Experiment_4/figures/stimuli/majority_b.png){ width=60% }", 
                        "![](Experiment_4/figures/stimuli/consensus_b.png){ width=60% }"))

# Use kable() to create the table and print it as Markdown
kableExtra::kable(image_paths, format = "markdown",
                  col.names = c("Level", "Version a)", "Version b)"), 
                  align = "c",
                  caption = "All stimuli by levels of convergence") %>%
  column_spec(1, width = "2em") %>%
  column_spec(2, width = "15em") %>%
  column_spec(3, width = "15em")

@@

Table \@ref(tab:exp4-table) contains descriptive results and Figure \@ref(fig:exp4-plot) visualizes the results.

@@

(ref:exp4-plot) Distributions of accuracy and competence by level of convergence.

```{r exp4-plot, fig.cap="(ref:exp4-plot)"}
# plot for accuracy
plot_accuracy <- ggplot(exp4,
       aes(x = convergence_categorical, y = accuracy, fill = convergence_categorical)) +
  geom_half_violin(position = position_nudge(x = -.2),
                   adjust=2, alpha = .8,
                   side = "l") +
  stat_summary(fun = "mean", geom = "point", size = 1, shape = 21) +
  stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
  # Add nice labels
  labs(x = "Convergence", y = "Accuracy") +
  scale_fill_viridis_d(option = "plasma", begin = 0.1) +
  guides(fill = FALSE) +
  plot_theme + 
  theme(axis.text.x = element_text(angle = 20, hjust = 1)) +  
  rremove("xlab")   # Remove x-axis label

# plot for competence
plot_competence <- ggplot(exp4,
       aes(x = convergence_categorical, y = competence, fill = convergence_categorical)) +
  geom_half_violin(position = position_nudge(x = -.2),
                   adjust=2, alpha = .8,
                   side = "l") +
  stat_summary(fun = "mean", geom = "point", size = 1, shape = 21) +
  stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
  # Add nice labels
  scale_y_continuous(limits = c(1,7), breaks = seq(1,7)) +
  labs(x = "Convergence", y = "Competence") +
  scale_fill_viridis_d(option = "plasma", begin = 0.1) +
  guides(fill = FALSE) +
  plot_theme + 
  theme(axis.text.x = element_text(angle = 20, hjust = 1)) +  
  rremove("xlab")   # Remove x-axis label

ggarrange(plot_accuracy, plot_competence) %>% 
  annotate_figure(bottom = textGrob("Convergence",gp = gpar(cex = 1, fontface = "bold")))
```

## Comparison with simulation

We compared the accuracy and competence ratings of the participants to actual accuracy and competence values from simulated data. The data was generated using the model described in the main paper, and assuming a uniform competence distribution. Compared to this data generating model, participants underestimate the effect of convergence for both accuracy and competence, but more for accuracy. Table \@ref(tab:model-vs-participant-table) compares the results of regressions on participant data and regressions on simulated data. Fig. \@ref(fig:exp4-model) visualizes the results.

```{r}
# read simulated data from .csv files
sim_experiment_4 <- read_csv("Experiment_4/data/sim_experiment_4.csv")
```

```{r}
# Run model on simulated data
regression_data <- sim_experiment_4 %>%
  mutate(
    # make numeric version of convergence
    convergence = case_when( 
      constellation == "minority" ~ 0, 
      constellation == "dissensus" ~ 1,
      constellation == "majority" ~ 2,
      constellation == "consensus" ~ 3), 
    # scale accuracy to reach from 0 to 100 (instead from 0 to 1)
    average_accuracy = average_accuracy*100,
    # scale competence to reach from 1 to 7 (instead of 0 to 1)
    average_relative_competence = 6*average_relative_competence + 1 
  )

accuracy_model <- lm(average_accuracy ~ convergence, 
                     data = regression_data)
competence_model <- lm(average_relative_competence ~ convergence, 
                       data = regression_data)
```

```{r}
# read participant data
d <- exp4
```

```{r model-vs-participant-table}
# Calculate models for participants

# model for accuracy
# random intercept and slope by participants
accuracy_participants <- lmer(accuracy ~ convergence + (1 + convergence | id), 
                                 data = d)
# model for competence
# random intercept and slope by participants
competence_participants <- lmer(competence ~ convergence + 
                           (1 + convergence | id), data = d)

# main result table
modelsummary::modelsummary(list("Accuracy" = accuracy_participants, 
                                "Competence" = competence_participants,
                                "Accuracy" = accuracy_model, 
                                "Competence" = competence_model
                                ),
                           title = 'Participants vs. Model (Exp. 4)', 
                           stars = TRUE) %>%
  kableExtra::add_header_above(c(" " = 1, "Participants" = 2, "Model" = 2))
```

```{r, echo=FALSE}
# Participant data

# plot for accuracy
plot_accuracy <- ggplot(d,
       aes(x = convergence_categorical, y = accuracy, fill = convergence_categorical)) +
  geom_half_violin(position = position_nudge(x = -.2),
                   adjust=2, alpha = .8,
                   side = "l") +
  stat_summary(fun = "mean", geom = "point", size = 1, shape = 21) +
  stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
  # Add nice labels
  labs(x = "Convergence", y = "Accuracy") +
  scale_fill_viridis_d(option = "plasma", begin = 0.1) +
  guides(fill = FALSE) +
  plot_theme + 
  theme(axis.text.x = element_text(angle = 20, hjust = 1))

# plot for competence
plot_competence <- ggplot(d,
       aes(x = convergence_categorical, y = competence, fill = convergence_categorical)) +
  geom_half_violin(position = position_nudge(x = -.2),
                   adjust=2, alpha = .8,
                   side = "l") +
  stat_summary(fun = "mean", geom = "point", size = 1, shape = 21) +
  stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
  # Add nice labels
  labs(x = "Convergence", y = "Competence") +
  scale_fill_viridis_d(option = "plasma", begin = 0.1) +
  guides(fill = FALSE) +
  plot_theme + 
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

```{r}
# Model data
plot_accuracy_model <- plot_results(sim_experiment_4, outcome = "accuracy")
plot_competence_model <- plot_results(sim_experiment_4, outcome = "competence")
```

(ref:exp4-model) Comparison of accuracy (top) and competence (bottom) ratings in participant data (left) to observed accuracy in simulated data (right), by level of convergence.

```{r exp4-model, fig.cap="(ref:exp4-model)"}
# Combine participant and model
# accuracy
plot_accuracy <- plot_accuracy + ggtitle("Participants") + labs(caption = NULL)
plot_accuracy_model <- plot_accuracy_model + ggtitle("Model") + labs(caption = NULL)

# competence
plot_competence <- plot_competence 
plot_competence_model <- plot_competence_model

(plot_accuracy + plot_accuracy_model) / (plot_competence + plot_competence_model)
```

### 2024-03-26 appendix_exp5.Rmd
major changes before adding analytical part

We manipulated convergence within participants in the same way we did in experiment 4. In addition, between participants, we manipulated informational dependence, akin to experiment 3 (Table \@ref(exp5-condition)). In the biased condition, experts were described to gain personally from recommending a certain investment option - but without specifying what that option is. In the independent condition, there was no such conflict of interest and experts were described as independent.

```{r exp5-condition}
# Participants read only one of these introductions before seeing the sets of estimates, depending on which condition they had been assigned to
data.frame(
  Condition = c("Independence condition", "Conflict of interest condition"),
  Description = c(
    "The three advisors are independent of each other, and have no conflict of interest in making investment recommendations.",
    "The three advisors have already invested in one of the three options, the same option for all three. As a result, they have an incentive to push that option in their recommendations."
  )
) #%>% 
  # apa_table(align = c("m{3cm}", "m{12cm}")) 
```

@@

## Stimuli

Our design required that each participant sees four different sets of predictions--two convergent and two divergent ones. We generated new stimuli: As in experiment 1, estimates would appear on a scale from 1000 to 2000. By contrast with experiment 1, we generated the sets of estimates with random draws from uniform distributions (instead of normal distributions). We varied the range of these distributions according to convergence (60 for convergence, 600 for divergence). Switching from normal distributions to uniform distributions made 'unlucky' draws in which conditions are visually not distinguishable less likely.

Similar to the previous experiments, we also vary the value on the prediction scale (from 1000 to 2000) across which the range is centered. Considering our within-participant design, this, again, made it seem more likely that participants understand each set of predictions as being the result of a different stock, with a different true value. In order to assure all random draws from the distributions would appear on the response scale, we constrained the center of the uniform distributions to lie between 1300 and 1700. We define four center values -- one per set of predictions -- that divide this interval in (rounded) quartiles (1300, 1430, 1570, 1700). Given a center and a range, we then draw the predictions from uniform distributions. For example, in a draw for a divergent set of estimates with a center of 1700, each value within a range of 1400 and 2000 is equally likely to get selected. To avoid that single draws overlap too much within the same set, we defined a minimum space of 5 between the three predictions of a set.

To minimize confounding of convergence with a certain placement of the center value, we paired center values with conditions such that each condition appears once in each half of the scale and each condition gets one of the extreme values. For example, in one set the convergence condition would get assigned center values of 1300 and 1570, the divergent condition center values of 1430 and 1700). We generated four such series (all possible combinations) and randomly assigned participants to one of them. Additionally, for each participant, we randomize the order of appearance of the sets of predictions within the respective series.

For each set of predictions, we calculated the empirical mean based on the randomly drawn estimates. In the conflict of interest condition, this mean was inserted as the value that participants were be told experts would gain from. Consequently, the convergent predictions converge around what is said to be the incentivized value for the experts to choose.

>>>>

We manipulated convergence within participants in the same way we did in experiment 4. In addition, between participants, we manipulated informational dependence, akin to experiment 3 (Table \@ref(tab:exp5-condition)). In the biased condition, experts were described to gain personally from recommending a certain investment option - but without specifying what that option is. In the independent condition, there was no such conflict of interest and experts were described as independent.

```{r exp5-condition}
# Participants read only one of these introductions before seeing the sets of estimates, depending on which condition they had been assigned to
data.frame(
  Condition = c("Independence condition", "Conflict of interest condition"),
  Description = c(
    "The three advisors are independent of each other, and have no conflict of interest in making investment recommendations.",
    "The three advisors have already invested in one of the three options, the same option for all three. As a result, they have an incentive to push that option in their recommendations."
  )
) %>% 
  apa_table(align = c("m{3cm}", "m{12cm}")) 
```

@@
